---
title: "Behind the Scenes of IMDb"
author: "Danica Miguel, Lizette Carpenter, and Emily Kim"
date: "May 1, 2018"
output: 
  html_document:
    theme: journal
    code_folding: hide
---

```{r message = FALSE, include = FALSE, warning = FALSE}
library(mdsr)
library(RMySQL)
library(ggplot2)
library(scales)
db <- dbConnect_scidb(dbname = "imdb")
```

```{r message=FALSE, include = FALSE, warning = FALSE}
class(db)
```

**Problem Statement:**
When googling [imdb](https://www.google.com/search?q=imdb&rlz=1C5CHFA_enUS721US721&oq=IMDB&aqs=chrome.0.0j69i60j69i59j69i60l3.2432j1j7&sourceid=chrome&ie=UTF-8), the first result is the IMDb’s [website](https://www.imdb.com/pressroom/about/?pf_rd_m=A2FGELUUNOQJNL&pf_rd_p=c1695c53-c70f-429d-859f-647489ac83de&pf_rd_r=F9J4ZH0MYVAVCFF2GPJ9&pf_rd_s=right-1&pf_rd_t=60601&pf_rd_i=pressroom&ref_=fea_pr_pr_lk2) where it briefly explains, “IMDb, the world's most popular and authoritative source for movie, TV and celebrity content.” In our investigation, we want to look at the question "to what extent is IMDb truly worldwide?", and to answer this question, we will be looking at different languages. Each member of our group is bilingual and shares the ability of enjoying movies and TV series produced in languages other than English. Thus, our interest is to see how the representation of movies and TV series produced in non-English languages has changed over the last 100 years in IMDb’s database.  


```{r message=FALSE, warning = FALSE}
###total number of movies in imdb
total_entertainment <- db %>% 
  dbGetQuery("SELECT production_year, COUNT(*) as total_entertainment
FROM imdb.title
WHERE kind_id = 1
GROUP BY production_year
ORDER BY production_year DESC;")

###number of movies for each specified language in imdb
all_language_movies <- db%>%
  dbGetQuery("SELECT production_year, SUM(info LIKE '%English%') AS English, SUM(info LIKE '%Tagalog%') AS Tagalog, SUM(info LIKE '%Spanish%') AS Spanish, SUM(info LIKE '%Korean%') as Korean 
FROM imdb.movie_info
JOIN title on movie_info.movie_id = title.id
WHERE info_type_id = 4
AND kind_id = 1
GROUP BY production_year;")

###number of tv series for each specified language in imdb
all_language_tv <- db%>%
  dbGetQuery("SELECT production_year, SUM(info LIKE '%English%') AS English, SUM(info LIKE '%Tagalog%') AS Tagalog, SUM(info LIKE '%Spanish%') AS Spanish, SUM(info LIKE '%Korean%') as Korean 
FROM imdb.movie_info
JOIN title on movie_info.movie_id = title.id
WHERE info_type_id = 4
AND kind_id = 2
GROUP BY production_year;")

###combining production years for each language for movies
all_movies_long <- all_language_movies %>%
  gather(key = "languages", value = "total", English:Korean) %>%
  arrange(production_year)
```

###Title for movies plot 
```{r message=FALSE, warning = FALSE}
###plot for movies
ggplot(all_movies_long, aes(x= production_year, y = total)) +
  geom_line(aes(color = factor(languages)), alpha = 1) +
  xlim(1917,2017)
```
As seen in this data graphic, the dominating language is English, and thus movies that are in English are the most represented in the IMDb database. For us, we thought it would be especially interesting to look at the number of movies of English, Korean, Spanish, and Tagalog movies, especially since we are able to speak these languages. The way it comes down to it, comparably, there are significantly less movies in the languages other than English. Although we do acknowledge that IMDb was created by an English man, and thus would probably have IMDb's database primarily from English movies, we thought that there is still a lack of representation of these different movies in different languages, especially when looking in the last 20 years or so. 

```{r message=FALSE, warning = FALSE}
###combining production years for each language for tv series
all_tv_long <- all_language_tv %>%
  gather(key = "languages", value = "total", English:Korean) %>%
  arrange(production_year)
```

###Title for tv series plot 
```{r message=FALSE, warning = FALSE}
###plot for tv series
ggplot(all_tv_long, aes(x= production_year, y = total)) +
  geom_line(aes(color = factor(languages)), alpha = 1) +
  scale_x_continuous(name = "Production Year",
                   limit = c(1917, 2017)) +
  scale_y_continuous(name = "Number of Movies") +
  scale_color_discrete(name = "Languages")
```

This idea is thus continued into the TV series. Can IMDb truly call itself "worldwide", despite the lack of other languages? 

```{r message=FALSE, warning = FALSE}
movies <- all_language_movies %>%
  left_join(total_entertainment, by="production_year")

```
#English Movies
```{r message=FALSE, warning = FALSE}
years <- filter(movies, production_year == "2017" | production_year == "2007" | production_year == "1997")

ggplot(years, aes(x = production_year, y = English/total_entertainment*100)) +
  geom_bar(stat = "identity",
           fill = "red1") +
  ggtitle("English Speaking Movies in IMDb")  +
  scale_x_continuous(name = "Production Year", 
                     breaks = c(1997, 2007, 2017, 10)) +
  scale_y_continuous(name = "% of English Movies in IMDb Database", 
                     limits = c(0, 100), 
                     breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100))
```

#Spanish Movies
```{r message = FALSE, warning = FALSE}
years <- filter(movies, production_year == "2017" | production_year == "2007" | production_year == "1997")

ggplot(years, aes(x = production_year, y = Spanish/total_entertainment*100)) +
  geom_bar(stat = "identity",
           fill = "turquoise1") +
  ggtitle("Spanish Speaking Movies in IMDb") +
  scale_x_continuous(name = "Production Year", 
                     breaks = c(1997, 2007, 2017, 10)) +
  scale_y_continuous(name = "% of Spanish Movies in IMDb Database", 
                     limits = c(0, 100), 
                     breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100))
```

#Tagalog Movies
```{r message = FALSE, warning = FALSE}
years <- filter(movies, production_year == "2017" | production_year == "2007" | production_year == "1997")

ggplot(years, aes(x = production_year, y = Tagalog/total_entertainment*100)) +
  geom_bar(stat = "identity",
           fill = "darkorchid4") +
  ggtitle("Tagalog Speaking Movies in IMDb") +
  scale_x_continuous(name = "Production Year", 
                     breaks = c(1997, 2007, 2017, 10)) +
  scale_y_continuous(name = "% of Tagalog Movies in IMDb Database", 
                     limits = c(0, 100), 
                     breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100))
```

#Korean Movies
```{r message = FALSE, warning = FALSE}
years <- filter(movies, production_year == "2017" | production_year == "2007" | production_year == "1997")

ggplot(years, aes(x = production_year, y = Korean/total_entertainment*100)) +
  geom_bar(stat = "identity",
           fill = "olivedrab4") +
  ggtitle("Korean Speaking Movies in IMDb") +
  scale_x_continuous(name = "Production Year", 
                     breaks = c(1997, 2007, 2017, 10)) +
  scale_y_continuous(name = "% of Korean Movies in IMDb Database", 
                     limits = c(0, 100), 
                     breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100))

```

